\huge A Usability Evaluation of Tor Launcher

### 2017-03-28 pets2017-paper/pets2017-paper.tex
kill an orphan, as requested by review

We recommend a gradual approach that starts with deploying design changes, measuring the impact of those changes, and cautiously incorporating automation into the interface only if the impact of those changes is still unsatisfactory.

>>>>

We recommend a gradual approach that starts with deploying design changes, measuring the impact of those changes, and cautiously incorporating automation if the impact of those changes is still unsatisfactory.
